%!TEX root = mcmpaper.tex
\section{Proposals}
Based on the above model as well as their analysis. In order to take full advantage of airport's security equipment and improve the efficiency of the staff and reduce the time of through the security zone and reduce the difference between each other. We would like to make the following recommendations to the safety management:
\begin{enumerate}
	\item Reasonable arrangements for flight time and the original peak hours of flights to be adjusted. Make the flight 24 hours a day evenly distributed. 
 	\item Make full use of equipment and staff in zone A. We can cancel the diversion in zone A, passengers who buy the pre-check service go to the pre-check channel in zone B.
 	\item Reasonably increase the number of equipment and staff in each zone. For example, for the study of the object O'Hare Airport, after our modeling and analysis we can see that zone A has 11 sets of equipment to identify passengers, zone B's regular channel has 18 sets of equipment to check baggage and passengers and pre-check channel has 6. Such a combination is more appropriate.
 	\item Reasonably increase the number of staff in the zone B to carry out physical examination of passengers to make full use of the conveyor belt efficiency and speed up the inspection speed of  zone B.
 	\item In the second improvement of question b, we find that passengers using pre-check channels don't spend less time than regular tourists. This may be related to the fact that more and more people in the USA are purchasing pre-check services and the probability of most of these people traveling by plane is very high. So the pre-check channel has not been fully utilized, when the passenger traffic is large, the airport can open serveral pre-check channel.
 	\item Airport security department needs to properly adjust the security procedures according to the differences between regions and regional culture. For example, people in some region may like to bring a lot of belongings, then it is appropriate to increase the zone B equipment and the number of staff and so on. Of course these improvements should be based on the specific regional culture and the specific situation. We need to try again and again to get the final program.
\end{enumerate}

